---
title: "Digitalisation vocabulary"
author: "Kim Lea Rothe"
date: "2023-01-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)

library(tidyverse)
library(here)
library(pdftools)
library(tidytext)
library(textdata)
library(ggwordcloud)

```

## Load documents in R

In a first step, 50 documents are loaded into a dataframe in R. The full text of the documents are then prepared for a wordcount to figure out which words are most frequently used. Numbers and stop words are eliminated in the preparation.

```{r get documents}
list <- (1:50)
i = 1
df <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(df) <- c('document_text', 'text_full')

for (number in list) {
  document_name = list[[i]]
  name = toString(document_name)
  document_path <- here("data-digitalisation",paste0(name))
  document_text <- pdf_text(document_path)
  document_df <- data.frame(document_text) %>% 
    mutate(text_full = str_split(document_text, pattern = '\\n')) %>% 
    unnest(text_full) %>% 
    mutate(text_full = str_trim(text_full))
  df <- rbind(df, document_df)
  i <- i+1
  }
```

```{r tokenize}
digitalisation_tokens <- df %>% 
  unnest_tokens(word, text_full)
```

```{r stopwords}
digitalisation_stop <- digitalisation_tokens %>% 
  anti_join(stop_words) 
```

```{r skip-numbers}
digitalisation_no_numeric <- digitalisation_stop %>% 
  filter(is.na(as.numeric(word)))
```

## Wordcount and Visualization

The words are then counted and visualized in a word cloud showing the 100 most used words.

```{r count-words}
digitalisation_wc <- digitalisation_no_numeric %>% 
  count(word) %>% 
  arrange(-n)
digitalisation_wc
```

```{r wordcloud-prep}

digitalisation_top100 <- digitalisation_no_numeric %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(100)
```

```{r wordcloud}
ggplot(data = digitalisation_top100, aes(label = word, size = n)) +
  geom_text_wordcloud_area(aes(color = n), shape = "oval") +
  scale_size_area(max_size = 8) +
  scale_color_gradientn(colors = c("darkgreen","blue","red")) +
  theme_minimal()
```
